Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
remove duplicate comment
added references

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is a broadly investigated, 
however the presence of digital control architectures is exacerbated by specific artefacts,  
%specific to digital control, 
such as the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
Whilst the research on digital control is well developed [Astrom book on digital control], 
automated and sound control synthesis is a challenging task. 
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.

@@

\todo{this section is unclear and probably needs to move somewhere else as it is only relevant for the acceleration back end} 
\todo{yes, please reformat the discussion below so that it fits the discussion above. }

>>>>

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is a broadly investigated, 
however the presence of digital control architectures is exacerbated by specific artefacts,  
%specific to digital control, 
such as the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is a challenging task. 
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.

@@

\todo{yes, please reformat the discussion below so that it fits the discussion above. }
